---
title: "april-study-hall"
author: "Jamal Nimer"
date: "4/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(readxl)
library(reprex)
library(janitor)
library(gt)
library(shiny)
library(googlesheets4)
```

```{r}

# reads in from the "first_years"
# google sheet in the project drive

sheets_deauth()

ss = "https://docs.google.com/spreadsheets/d/1d8TlsQLzm15eSbcYhCPANcIUwWmMymRRwYBrUP3RtB8/edit?usp=sharing"

sheet <- read_sheet(ss) %>%
  clean_names() %>% 
  select(-timestamp,-email_address)


```




split the strings using the commas.
 
Reference the list of all the freshman. 

Cross-reference the names from the blocking group responses to the full list of students.

Assign a block id from the names.

Find out all the hoco members, and get housing assignments from them.

predicting race from name? 

Match on blocking group leader instead of blocking group name.

---------

create list of blocking group leaders

for loop and go through and assign each person to their blocking group leader

Empty dataframe > block leader, house, group size, > get block leader take blocking group leaders > take each person's list of block mate and corresponding blocking group leader 

Using google sheets:
- create a range of names from the first_years sheet
- create a range of names from the respondents sheet 
- using conditional formatting, check if the respondents range has an exact match in the first_years range and if the first_years range has an exact match in the respondents range (highlight exact matches in green, highlight unmatched data in both ranges in red)
- put red data from both ranges in a new sheet and try to find pairs. 



```{r}

View(sheet)

```



